---
title: "mev_context_gender_analysis"
author: "Leopold Roth"
date: "2024-09-24"
output: html_document
---

```{r setup, include=FALSE}
# Set global chunk options
knitr::opts_chunk$set(
  warning = FALSE,  # Suppress warnings
  message = FALSE,  # Suppress messages
  error = TRUE,     # Allow knitting to continue even with errors
  echo = TRUE       # Show code in the output (you can change this to FALSE if you don't want the code to show)
)
```

# packages
```{r message=FALSE, warning=FALSE}
library(MatrixModels)
library(dplyr)
library(readr)
library(ggplot2)
library(psych)
library(lavaan)
library(easystats)
library(semPlot)
library(reshape2)
library(misty)
library(foreign)
library(varhandle)
library(car)
library(eRm)
library(tidyr)
library(haven)
library(BayesFactor)
library(stringr)
library(patchwork)
library(afex)
library(emmeans)

```

# source functions from script
this 'runs' the script functions_run_first.R and saves work to do it yourself/otherwise can't knit (create markdown)
```{r, include=FALSE}
source("functions_run_first.R", local = knitr::knit_global())
```

# data
```{r}
df_care <- read_csv("mev_gender_care.csv")
df_work <- read_csv("mev_gender_work.csv")
```

# delete 2 columns in df_work (delete!)
delete this later
```{r}
#df_work <- df_work %>%
#  select(-c(C_Coop_loEf_m, C_Coop_hiEf_m))
```

# rename columns to match (correct spelling)
```{r}
# remove prefixes
colnames(df_care) <- sub("^C_", "", colnames(df_care))
colnames(df_work) <- sub("^W_", "", colnames(df_work))

# adjust names
df_care <- df_care %>%
  rename(Coop_LoEf_m = Coop_loEf_m,
         Coop_HiEf_m = Coop_hiEf_m,
         Coop_LoEf_f = Coop__LoEf_f,
         Coop_HiEf_f = Coop__HiEf_f)
```

# combine data wih identifier
```{r}
# identifier for studies
care <- rep(0, nrow(df_care))
work <- rep(1, nrow(df_work))

care_0_work_1 <- c(care, work)

# merge datasets
df <- rbind(df_care, df_work)

# add identifier
df$care_0_work_1 <- care_0_work_1
```

# compute gender identifier
```{r}
df$male_0_female_1 <- ifelse(is.na(df$Time_Vign_male_First_Click), 1, 0)
```

# prepare for cleaning
```{r}
# merge attention checks in one variable
df <- df %>%
  mutate(AC1 = coalesce(AC_f_1, AC_m_1),
         AC2 = coalesce(AC_f_2, AC_m_2))

# remove attention checks by gender
df <- df %>%
  select(-c(AC_f_1, AC_m_1, AC_f_2, AC_m_2))

# use data cleaning function (currently deactivated, because otherwise only 12 cases left)
# df <- clean_data(df)

# adjust column names
colnames(df) <- gsub("\\.0$", "", colnames(df))
colnames(df) <- gsub("(_m|_f|_m$|_f$)", "", colnames(df))

duplicated_columns <- colnames(df)[duplicated(colnames(df))]

# Temporarily rename duplicated columns to prevent conflict
colnames(df) <- make.unique(colnames(df))

# Loop through each base name and merge columns
for (col_name in unique(duplicated_columns)) {
  # Find all matching columns (the ones that were originally duplicates)
  matching_cols <- grep(paste0("^", col_name, "(\\.\\d+)?$"), colnames(df), value = TRUE)
  
  # Check if there are at least two columns to merge
  if (length(matching_cols) > 1) {
    # Merge the columns using coalesce
    df[[col_name]] <- coalesce(!!!df[matching_cols])
    
    # Optionally remove the temporary duplicates after merging, except the first one
    df <- df %>% select(-one_of(matching_cols[-1]))
  }
}

```

# reliabilities
## core goodness
### low effort
```{r}
#alpha
psych::alpha(df %>% select(c(Ch_LoEf_3, Ch_LoEf_9, Ch_LoEf_11, Ch_LoEf_10, Ch_LoEf_13, Ch_LoEf_14
)))[[1]]
#omega
psych::omega(df %>% select(c(Ch_LoEf_3, Ch_LoEf_9, Ch_LoEf_11, Ch_LoEf_10, Ch_LoEf_13, Ch_LoEf_14
)))[[1]]
```

### high effort
```{r}
#alpha
psych::alpha(df %>% select(c(Ch_HiEf_3, Ch_HiEf_9, Ch_HiEf_11, Ch_HiEf_10, Ch_HiEf_13, Ch_HiEf_14
)))[[1]]
#omega
psych::omega(df %>% select(c(Ch_HiEf_3, Ch_HiEf_9, Ch_HiEf_11, Ch_HiEf_10, Ch_HiEf_13, Ch_HiEf_14
)))[[1]]
```

## value commitment
### low effort
```{r}
#alpha
psych::alpha(df %>% select(c(Ch_LoEf_1, Ch_LoEf_5, Ch_LoEf_15, Ch_LoEf_8, Ch_LoEf_4, Ch_LoEf_12, Ch_LoEf_7)))[[1]]
#omega
psych::omega(df %>% select(c(Ch_LoEf_1, Ch_LoEf_5, Ch_LoEf_15, Ch_LoEf_8, Ch_LoEf_4, Ch_LoEf_12, Ch_LoEf_7)))[[1]]
```

### high effort
```{r}
#alpha
psych::alpha(df %>% select(c(Ch_HiEf_1, Ch_HiEf_5, Ch_HiEf_15, Ch_HiEf_8, Ch_HiEf_4, Ch_HiEf_12, Ch_HiEf_7)))[[1]]
#omega
psych::omega(df %>% select(c(Ch_HiEf_1, Ch_HiEf_5, Ch_HiEf_15, Ch_HiEf_8, Ch_HiEf_4, Ch_HiEf_12, Ch_HiEf_7)))[[1]]
```

# clean data
- no country filter: done through Prolific
- every variable was existet for female and male and had to be unified and connected
- difference score function: filters out participants who thought that the low effort condition was more/equally effortful than the high effort condition
```{r}
# use preparation function
df <- preparation(df)

# use difference score function
df <- difference_scores(df)
```

# prepare analysis
## keep needed columns

```{r}
# correction from name unification above
df <- df %>% rename(male_0_female_1 = male_0emale_1)

# keep needed columns for analysis
df <- df %>% 
    select(c(
      ResponseId, ends_with("_lo"), ends_with("_he"),starts_with("FW"), ends_with("_diff"),
      effort_check,Age, Gen, care_0_work_1, male_0_female_1
    ))
```

## demographic analysis
```{r}
# describe age for complete sample and by context
# describe age by context
age_summary_by_group <- df %>%
  group_by(care_0_work_1) %>%
  summarise(
    count = n(),
    mean_age = mean(Age, na.rm = TRUE),
    median_age = median(Age, na.rm = TRUE),
    min_age = min(Age, na.rm = TRUE),
    max_age = max(Age, na.rm = TRUE),
    sd_age = sd(Age, na.rm = TRUE)
  )

# Summarize Age across the whole sample
age_summary_total <- df %>%
  summarise(
    Group = "Total",  # Label the overall summary as 'Total'
    count = n(),
    mean_age = mean(Age, na.rm = TRUE),
    median_age = median(Age, na.rm = TRUE),
    min_age = min(Age, na.rm = TRUE),
    max_age = max(Age, na.rm = TRUE),
    sd_age = sd(Age, na.rm = TRUE)
  )

# Combine the group summary and total summary into one data frame
age_summary_combined <- bind_rows(age_summary_by_group, age_summary_total)

# gender by context
# work
# Create a cross-tabulation
cross_tab <- table( df_work$Gen)

# Convert the cross-tabulation to percentages
percentage_cross_tab <- round(prop.table(cross_tab) * 100,2)

# View the cross-tabulation with percentages
print(percentage_cross_tab)

# care
# Create a cross-tabulation
cross_tab <- table( df_care$Gen)

# Convert the cross-tabulation to percentages
percentage_cross_tab <- round(prop.table(cross_tab) * 100,2)

# View the cross-tabulation with percentages
print(percentage_cross_tab)

#gender complete sample
# Create a cross-tabulation
cross_tab <- table(df$Gen)

# Convert the cross-tabulation to percentages
percentage_cross_tab <- round(prop.table(cross_tab) * 100,2)

# View the cross-tabulation with percentages
print(percentage_cross_tab)
```

## split data again by context for analysis
```{r}
df_care <- subset(df, care_0_work_1 == 0)
df_work <- subset(df, care_0_work_1 == 1)
```

## descriptive: means
get all descriptives of everything and filter for what is needed
```{r}
means_all <- rownames_as_column(psych::describe(df))
means_care <- rownames_as_column(psych::describe(df_care))
means_work <- rownames_as_column(psych::describe(df_work))
```

## shortened descriptives for report
```{r}
# work context
short_work <- means_work %>%
  select(c(rowname, mean, sd)) %>%
  filter(grepl("^(core_|value_|warmth_|competence_|pay_|cooperation_)", rowname) & 
         !grepl("_diff$", rowname)) %>%
  mutate(
    sort_key = case_when(
      grepl("^core_", rowname) ~ 1,
      grepl("^value_", rowname) ~ 2,
      grepl("^warmth_", rowname) ~ 3,
      grepl("^competence_", rowname) ~ 4,
      grepl("^pay_", rowname) ~ 5,
      grepl("^cooperation_", rowname) ~ 6
    )
  ) %>%
  arrange(sort_key) %>%
  select(-sort_key)  # Remove the sorting key column

short_work$mean <- round(short_work$mean,2)
short_work$sd <- round(short_work$sd,2)

# care context
short_care <- means_care %>%
  select(c(rowname, mean, sd)) %>%
  filter(grepl("^(core_|value_|warmth_|competence_|pay_|cooperation_)", rowname) & 
         !grepl("_diff$", rowname)) %>%
  mutate(
    sort_key = case_when(
      grepl("^core_", rowname) ~ 1,
      grepl("^value_", rowname) ~ 2,
      grepl("^warmth_", rowname) ~ 3,
      grepl("^competence_", rowname) ~ 4,
      grepl("^pay_", rowname) ~ 5,
      grepl("^cooperation_", rowname) ~ 6
    )
  ) %>%
  arrange(sort_key) %>%
  select(-sort_key)  # Remove the sorting key column

short_care$mean <- round(short_care$mean,2)
short_care$sd <- round(short_care$sd,2)

```

# main analysis: Aim 1
## comparisons: core goodness
```{r}
#care
cg_care <- as.data.frame(report::report(t.test(df_care$core_good_lo, df_care$core_good_he, paired = TRUE)))
cg_care <- cg_care %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
cg_care$BF <- as.data.frame(ttestBF(x = df_care$core_good_lo, y = df_care$core_good_he, paired = TRUE))[[1]]

#work
cg_work <- as.data.frame(report::report(t.test(df_work$core_good_lo, df_work$core_good_he, paired = TRUE)))
cg_work <- cg_work %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
cg_work$BF <- as.data.frame(ttestBF(x = df_work$core_good_lo, y = df_work$core_good_he, paired = TRUE))[[1]]

#combine results
cg_results <- bind_rows(cg_care, cg_work) #using more flexible dplyr function; rbind had trouble with row.names
cg_results$target <- rep("core_goodness",nrow(cg_results)) #add column to mention DV
rm(list=c("cg_care","cg_work")) #removes non-needed dfs
```

## comparisons: value commitment
```{r}
#care
vc_care <- as.data.frame(report::report(t.test(df_care$value_comm_lo, df_care$value_comm_he, paired = TRUE)))
vc_care <- vc_care %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
vc_care$BF <- as.data.frame(ttestBF(x = df_care$value_comm_lo, y = df_care$value_comm_he, paired = TRUE))[[1]]

#work
vc_work <- as.data.frame(report::report(t.test(df_work$value_comm_lo, df_work$value_comm_he, paired = TRUE)))
vc_work <- vc_work %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
vc_work$BF <- as.data.frame(ttestBF(x = df_work$value_comm_lo, y = df_work$value_comm_he, paired = TRUE))[[1]]

#combine results
vc_results <- bind_rows(vc_care, vc_work) #using more flexible dplyr function; rbind had trouble with row.names
vc_results$target <- rep("value_commness",nrow(vc_results)) #add column to mention DV
rm(list=c("vc_care","vc_work")) #removes non-needed dfs
```

## comparisons: warmth
```{r}
#care
wa_care <- as.data.frame(report::report(t.test(df_care$warmth_lo, df_care$warmth_he, paired = TRUE)))
wa_care <- wa_care %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
wa_care$BF <- as.data.frame(ttestBF(x = df_care$warmth_lo, y = df_care$warmth_he, paired = TRUE))[[1]]

#work
wa_work <- as.data.frame(report::report(t.test(df_work$warmth_lo, df_work$warmth_he, paired = TRUE)))
wa_work <- wa_work %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
wa_work$BF <- as.data.frame(ttestBF(x = df_work$warmth_lo, y = df_work$warmth_he, paired = TRUE))[[1]]

#combine results
wa_results <- bind_rows(wa_care, wa_work) #using more flexible dplyr function; rbind had trouble with row.names
wa_results$target <- rep("warmthness",nrow(wa_results)) #add column to mention DV
rm(list=c("wa_care","wa_work")) #removes non-needed dfs
```

## comparisons: competence
```{r}
#care
co_care <- as.data.frame(report::report(t.test(df_care$competence_lo, df_care$competence_he, paired = TRUE)))
co_care <- co_care %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
co_care$BF <- as.data.frame(ttestBF(x = df_care$competence_lo, y = df_care$competence_he, paired = TRUE))[[1]]

#work
co_work <- as.data.frame(report::report(t.test(df_work$competence_lo, df_work$competence_he, paired = TRUE)))
co_work <- co_work %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
co_work$BF <- as.data.frame(ttestBF(x = df_work$competence_lo, y = df_work$competence_he, paired = TRUE))[[1]]

#combine results
co_results <- bind_rows(co_care, co_work) #using more flexible dplyr function; rbind had trouble with row.names
co_results$target <- rep("competence",nrow(co_results)) #add column to mention DV
rm(list=c("co_care","co_work")) #removes non-needed dfs
```

## comparisons: pay deservingness
```{r}
#care
pd_care <- as.data.frame(report::report(t.test(df_care$pay_deservingness_lo, df_care$pay_deservingness_he, paired = TRUE)))
pd_care <- pd_care %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
pd_care$BF <- as.data.frame(ttestBF(x = df_care$pay_deservingness_lo, y = df_care$pay_deservingness_he, paired = TRUE))[[1]]

#work
pd_work <- as.data.frame(report::report(t.test(df_work$pay_deservingness_lo, df_work$pay_deservingness_he, paired = TRUE)))
pd_work <- pd_work %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
pd_work$BF <- as.data.frame(ttestBF(x = df_work$pay_deservingness_lo, y = df_work$pay_deservingness_he, paired = TRUE))[[1]]

#combine results
pd_results <- bind_rows(pd_care, pd_work) #using more flexible dplyr function; rbind had trouble with row.names
pd_results$target <- rep("pay_deservingness",nrow(pd_results)) #add column to mention DV
rm(list=c("pd_care","pd_work")) #removes non-needed dfs
```

## comparisons: cooperation
```{r}
#care
cp_care <- as.data.frame(report::report(t.test(df_care$cooperation_lo, df_care$cooperation_he, paired = TRUE)))
cp_care <- cp_care %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
cp_care$BF <- as.data.frame(ttestBF(x = df_care$cooperation_lo, y = df_care$cooperation_he, paired = TRUE))[[1]]

#work
cp_work <- as.data.frame(report::report(t.test(df_work$cooperation_lo, df_work$cooperation_he, paired = TRUE)))
cp_work <- cp_work %>% select(p, Cohens_d, Cohens_d_CI_low, Cohens_d_CI_high)
cp_work$BF <- as.data.frame(ttestBF(x = df_work$cooperation_lo, y = df_work$cooperation_he, paired = TRUE))[[1]]

#combine results
cp_results <- bind_rows(cp_care, cp_work) #using more flexible dplyr function; rbind had trouble with row.names
cp_results$target <- rep("cooperation",nrow(cp_results)) #add column to mention DV
rm(list=c("cp_care","cp_work")) #removes non-needed dfs
```

### combine t-test results
```{r}
#combine results
comp_results <- bind_rows(cg_results,
                      vc_results,
                      wa_results,
                      co_results,
                      pd_results,
                      cp_results)

#add names list
samples <- c("care","work")
comp_results$context <- rep(samples,6)

comp_results <- comp_results %>% #rounds all numeric variables to 3 decimals
  mutate_if(is.numeric, round, digits = 3)

#this makes the transfer to word easier
##open excel, find/replace comma with point, copy, paste, correct format
#writexl::write_xlsx(comp_results, "t-results.xlsx")

#remove non-needed objects
rm(list = c("cg_results","vc_results","pd_results","wa_results","co_results","cp_results","samples"))
```

# main analysis: Aim 2 (gender pay gap)
```{r}
# work context
## low effort
report::report(t.test(pay_deservingness_lo ~ male_0_female_1, data = df_work))
ttestBF(x = df_work$pay_deservingness_lo, y = df_work$male_0_female_1)
## high effort
report::report(t.test(pay_deservingness_he ~ male_0_female_1, data = df_work))
ttestBF(x = df_work$pay_deservingness_he, y = df_work$male_0_female_1)

# care context
## low effort
report::report(t.test(pay_deservingness_lo ~ male_0_female_1, data = df_care))
ttestBF(x = df_care$pay_deservingness_lo, y = df_care$male_0_female_1)
## high effort
report::report(t.test(pay_deservingness_he ~ male_0_female_1, data = df_care))
ttestBF(x = df_care$pay_deservingness_he, y = df_care$male_0_female_1)
```

# main analysis: Aim 2 ANOVA (work)
```{r}
# work/core goodness
## restructure data
df_long <- df_work %>%
  pivot_longer(cols = c(core_good_he, core_good_lo),
               names_to = "core_good_condition",
               values_to = "score")

## perform anova
anova_results <- aov_ez(
  id = "ResponseId",  # Assuming there's a subject ID column
  dv = "score",  # Dependent variable
  between = "male_0_female_1",  # Between-subjects factor
  within = "core_good_condition",  # Within-subjects factor
  data = df_long
)

## print results
print(anova_results)

## post-hoc test
post_hoc <- emmeans(anova_results, pairwise ~ core_good_condition | male_0_female_1, p.adjust = "tukey")
print(post_hoc)

## Bayesian posthoc BF (commented out, takes a while)
#df_long$male_0_female_1 <- as.factor(df_long$male_0_female_1)
#df_long$core_good_condition <- as.factor(df_long$core_good_condition)
#num_unique_ids <- length(unique(df_long$ResponseId))  # Assuming ResponseId is the column with unique IDs
#df_long$ID <- rep(seq(1, num_unique_ids), each = 2)
#df_long$ID <- as.factor(df_long$ID)
# Perform the Bayesian mixed ANOVA again
#bf_anova <- anovaBF(
#  score ~ core_good_condition * male_0_female_1 + ID,
#  data = df_long,
#  whichRandom = "ID"
#)

#summary(bf_anova)



df_plot <- df_work #define df for plotting

df_plot <- df_plot %>%
  mutate(male_0_female_1 = as.character(male_0_female_1)) %>%  # Convert to character
  mutate(male_0_female_1 = case_when(
    male_0_female_1 == "0" ~ "male",
    male_0_female_1 == "1" ~ "female",
    TRUE ~ male_0_female_1  # This handles any unexpected values
  ))

#apply function for restructuring and plotting data
plot_cg_work <- plot_violin_with_means(df_plot, c("core_good_lo", "core_good_he"), "core goodness")

print(plot_cg_work)

# work/value commitment
df_long <- df_work %>%
  pivot_longer(cols = c(value_comm_he, value_comm_lo),
               names_to = "value_comm_condition",
               values_to = "score")

# Perform the mixed ANOVA
anova_results <- aov_ez(
  id = "ResponseId",  # Assuming there's a subject ID column
  dv = "score",  # Dependent variable
  between = "male_0_female_1",  # Between-subjects factor
  within = "value_comm_condition",  # Within-subjects factor
  data = df_long
)

# Print the results
print(anova_results)

post_hoc <- emmeans(anova_results, pairwise ~ value_comm_condition | male_0_female_1, p.adjust = "tukey")
print(post_hoc)

## Bayesian posthoc BF (commented out, takes a while)
#df_long$male_0_female_1 <- as.factor(df_long$male_0_female_1)
#df_long$value_comm_condition <- as.factor(df_long$value_comm_condition)
#num_unique_ids <- length(unique(df_long$ResponseId))  # Assuming ResponseId is the column with unique IDs
#df_long$ID <- rep(seq(1, num_unique_ids), each = 2)
#df_long$ID <- as.factor(df_long$ID)
# Perform the Bayesian mixed ANOVA again
#bf_anova <- anovaBF(
#  score ~ value_comm_condition * male_0_female_1 + ID,
#  data = df_long,
#  whichRandom = "ID"
#)

#summary(bf_anova)

df_plot <- df_work #define df for plotting

df_plot <- df_plot %>%
  mutate(male_0_female_1 = as.character(male_0_female_1)) %>%  # Convert to character
  mutate(male_0_female_1 = case_when(
    male_0_female_1 == "0" ~ "male",
    male_0_female_1 == "1" ~ "female",
    TRUE ~ male_0_female_1  # This handles any unexpected values
  ))

#apply function for restructuring and plotting data
plot_vc_work <- plot_violin_with_means(df_plot, c("value_comm_lo", "value_comm_he"), "value commitment")

print(plot_vc_work)

combined_plot_work <- plot_cg_work / plot_vc_work #combine plots

ggsave("combined_plot_work.png", combined_plot_work, width = 8, height = 8, dpi = 300)
```

# main analysis: Aim 2 ANOVA (care)
```{r}
# care/core goodness
## restructure data
df_long <- df_care %>%
  pivot_longer(cols = c(core_good_he, core_good_lo),
               names_to = "core_good_condition",
               values_to = "score")

## perform anova
anova_results <- aov_ez(
  id = "ResponseId",  # Assuming there's a subject ID column
  dv = "score",  # Dependent variable
  between = "male_0_female_1",  # Between-subjects factor
  within = "core_good_condition",  # Within-subjects factor
  data = df_long
)

## print results
print(anova_results)

## post-hoc test
post_hoc <- emmeans(anova_results, pairwise ~ core_good_condition | male_0_female_1, p.adjust = "tukey")
print(post_hoc)

## Bayesian posthoc BF (commented out, takes a while)
#df_long$male_0_female_1 <- as.factor(df_long$male_0_female_1)
#df_long$core_good_condition <- as.factor(df_long$core_good_condition)
#num_unique_ids <- length(unique(df_long$ResponseId))  # Assuming ResponseId is the column with unique IDs
#df_long$ID <- rep(seq(1, num_unique_ids), each = 2)
#df_long$ID <- as.factor(df_long$ID)
# Perform the Bayesian mixed ANOVA again
#bf_anova <- anovaBF(
#  score ~ core_good_condition * male_0_female_1 + ID,
#  data = df_long,
#  whichRandom = "ID"
#)

#summary(bf_anova)



df_plot <- df_care #define df for plotting

df_plot <- df_plot %>%
  mutate(male_0_female_1 = as.character(male_0_female_1)) %>%  # Convert to character
  mutate(male_0_female_1 = case_when(
    male_0_female_1 == "0" ~ "male",
    male_0_female_1 == "1" ~ "female",
    TRUE ~ male_0_female_1  # This handles any unexpected values
  ))



#apply function for restructuring and plotting data
plot_cg_care <- plot_violin_with_means(df_plot, c("core_good_lo", "core_good_he"), "core goodness")

print(plot_cg_care)

# care/value commitment
df_long <- df_care %>%
  pivot_longer(cols = c(value_comm_he, value_comm_lo),
               names_to = "value_comm_condition",
               values_to = "score")

# Perform the mixed ANOVA
anova_results <- aov_ez(
  id = "ResponseId",  # Assuming there's a subject ID column
  dv = "score",  # Dependent variable
  between = "male_0_female_1",  # Between-subjects factor
  within = "value_comm_condition",  # Within-subjects factor
  data = df_long
)

# Print the results
print(anova_results)

post_hoc <- emmeans(anova_results, pairwise ~ value_comm_condition | male_0_female_1, p.adjust = "tukey")
print(post_hoc)

## Bayesian posthoc BF (commented out, takes a while)
#df_long$male_0_female_1 <- as.factor(df_long$male_0_female_1)
#df_long$value_comm_condition <- as.factor(df_long$value_comm_condition)
#num_unique_ids <- length(unique(df_long$ResponseId))  # Assuming ResponseId is the column with unique IDs
#df_long$ID <- rep(seq(1, num_unique_ids), each = 2)
#df_long$ID <- as.factor(df_long$ID)
# Perform the Bayesian mixed ANOVA again
#bf_anova <- anovaBF(
#  score ~ value_comm_condition * male_0_female_1 + ID,
#  data = df_long,
#  whichRandom = "ID"
#)

#summary(bf_anova)

df_plot <- df_care #define df for plotting

df_plot <- df_plot %>%
  mutate(male_0_female_1 = as.character(male_0_female_1)) %>%  # Convert to character
  mutate(male_0_female_1 = case_when(
    male_0_female_1 == "0" ~ "male",
    male_0_female_1 == "1" ~ "female",
    TRUE ~ male_0_female_1  # This handles any unexpected values
  ))

#apply function for restructuring and plotting data
plot_vc_care <- plot_violin_with_means(df_plot, c("value_comm_lo", "value_comm_he"), "value commitment")

print(plot_vc_care)

combined_plot_care <- plot_cg_care / plot_vc_care #combine plots

ggsave("combined_plot_care.png", combined_plot_care, width = 8, height = 8, dpi = 300)
```

# main analysis: Aim 3 (cooperation partner satisfaction)
```{r}
# work
## restructure data
df_long <- df_work %>%
  pivot_longer(cols = c(cooperation_he, cooperation_lo),
               names_to = "cooperation_condition",
               values_to = "score")

## perform anova
anova_results <- aov_ez(
  id = "ResponseId",  # Assuming there's a subject ID column
  dv = "score",  # Dependent variable
  between = "male_0_female_1",  # Between-subjects factor
  within = "cooperation_condition",  # Within-subjects factor
  data = df_long
)

## print results
print(anova_results)

## post-hoc test
post_hoc <- emmeans(anova_results, pairwise ~ cooperation_condition | male_0_female_1, p.adjust = "tukey")
print(post_hoc)

## Bayesian posthoc BF (commented out, takes a while)
#df_long$male_0_female_1 <- as.factor(df_long$male_0_female_1)
#df_long$cooperation_condition <- as.factor(df_long$cooperation_condition)
#num_unique_ids <- length(unique(df_long$ResponseId))  # Assuming ResponseId is the column with unique IDs
#df_long$ID <- rep(seq(1, num_unique_ids), each = 2)
#df_long$ID <- as.factor(df_long$ID)
# Perform the Bayesian mixed ANOVA again
#bf_anova <- anovaBF(
#  score ~ cooperation_condition * male_0_female_1 + ID,
#  data = df_long,
#  whichRandom = "ID"
#)

#summary(bf_anova)



df_plot <- df_work #define df for plotting

df_plot <- df_plot %>%
  mutate(male_0_female_1 = as.character(male_0_female_1)) %>%  # Convert to character
  mutate(male_0_female_1 = case_when(
    male_0_female_1 == "0" ~ "male",
    male_0_female_1 == "1" ~ "female",
    TRUE ~ male_0_female_1  # This handles any unexpected values
  ))

#apply function for restructuring and plotting data
plot_cp_work <- plot_violin_with_means(df_plot, c("cooperation_lo", "cooperation_he"), "cooperation")



# care
## restructure data
df_long <- df_care %>%
  pivot_longer(cols = c(cooperation_he, cooperation_lo),
               names_to = "cooperation_condition",
               values_to = "score")

## perform anova
anova_results <- aov_ez(
  id = "ResponseId",  # Assuming there's a subject ID column
  dv = "score",  # Dependent variable
  between = "male_0_female_1",  # Between-subjects factor
  within = "cooperation_condition",  # Within-subjects factor
  data = df_long
)

## print results
print(anova_results)

## post-hoc test
post_hoc <- emmeans(anova_results, pairwise ~ cooperation_condition | male_0_female_1, p.adjust = "tukey")
print(post_hoc)

## Bayesian posthoc BF (commented out, takes a while)
#df_long$male_0_female_1 <- as.factor(df_long$male_0_female_1)
#df_long$cooperation_condition <- as.factor(df_long$cooperation_condition)
#num_unique_ids <- length(unique(df_long$ResponseId))  # Assuming ResponseId is the column with unique IDs
#df_long$ID <- rep(seq(1, num_unique_ids), each = 2)
#df_long$ID <- as.factor(df_long$ID)
# Perform the Bayesian mixed ANOVA again
#bf_anova <- anovaBF(
#  score ~ cooperation_condition * male_0_female_1 + ID,
#  data = df_long,
#  whichRandom = "ID"
#)

#summary(bf_anova)



df_plot <- df_care #define df for plotting

df_plot <- df_plot %>%
  mutate(male_0_female_1 = as.character(male_0_female_1)) %>%  # Convert to character
  mutate(male_0_female_1 = case_when(
    male_0_female_1 == "0" ~ "male",
    male_0_female_1 == "1" ~ "female",
    TRUE ~ male_0_female_1  # This handles any unexpected values
  ))

#apply function for restructuring and plotting data
plot_cp_care <- plot_violin_with_means(df_plot, c("cooperation_lo", "cooperation_he"), "cooperation")

ggsave("cooperation_plot_work.png", plot_cp_work, width = 8, height = 4, dpi = 300)
ggsave("cooperation_plot_care.png", plot_cp_care, width = 8, height = 4, dpi = 300)
```

